### 2024-12-01 paper/paper.qmd
update model set-up

library(readr)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-correlation
#| fig-cap: "Correlation"

#mosaic plot
library(vcd)
table_data <- xtabs(~ cut + clarity + color, data = cleaned_data)

highlighting_colors <- grDevices::rainbow(8, alpha = 0.5)  # alpha 
options(repr.plot.width = 12, repr.plot.height = 12)  # 宽度和高度可根据需要调整

mosaic(~ cut + clarity + color, data = table_data,
       highlighting = "color",                      # 设置高亮变量为 color
       highlighting_fill = highlighting_colors,    # 使用生成的浅色彩虹
       direction = c("h", "v", "h"), # 控制变量的排列方向
       main = "Relationship Between Cut, Clarity, and Color")

@@

## Data Cleaning {#sec-datacleaning}

### Data Split

@@

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 
数据分布不均

@@

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

@@

# Additional data details

@@

@@

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

>>>>

library(readr)
library(arrow)
library(here)
library(ggplot2)
library(patchwork)
library(ggplot2)

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-correlation_heat
#| fig-cap: "Correlation: Heat Graph"

# 按 cut, color, 和 clarity 聚合 carat_size 的均值
agg_data <- aggregate(carat_size ~ cut + color + clarity, data = cleaned_data, FUN = mean)

#agg_data <- aggregate(carat_size ~ cut + color + clarity, data = #cleaned_data, FUN = median)

# 绘制分面热图
ggplot(agg_data, aes(x = cut, y = color, fill = carat_size)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "pink") +
  facet_wrap(~ clarity) + # 按 clarity 分面
  labs(title = "Heatmap of Carat Size by Cut, Color, and Clarity",
       x = "Cut", y = "Color", fill = "Mean Carat Size") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 20, hjust = 1))+
  theme(axis.text.y = element_text(size = 6))

@@

@@

## Data preparation
包括如何处理reponse来符合gamma。详细请见appendix

@@

Define \( y_i \) as the price of the \( i \)-th diamond. Predictors include:

\begin{align} 
- \( x_{1i} \): The carat size of the diamond (in carats).
- \( x_{2i} \): The color grade of the diamond (categorical).
- \( x_{3i} \): The cut grade of the diamond (categorical).
- \( x_{4i} \): The clarity grade of the diamond (categorical).

**Model Structure**:
1. **Response Distribution**:  
   \( y_i \mid \mu_i, \phi \sim \text{Gamma}(\mu_i, \phi) \),  
   where \( \mu_i \) is the mean price and \( \phi \) is the dispersion parameter.

2. **Link Function**:  
   \( \log(\mu_i) = \beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il} \).

   - \( \beta_0 \): Intercept term.  
   - \( \beta_1 \): Effect of carat size.  
   - \( \beta_{2j}, \beta_{3k}, \beta_{4l} \): Effects of color, cut, and clarity, respectively.

3. **Mean Price**:  
   \( \mu_i = \exp(\beta_0 + \beta_1 x_{1i} + \sum_{j} \beta_{2j} \cdot \text{color}_{ij} + \sum_{k} \beta_{3k} \cdot \text{cut}_{ik} + \sum_{l} \beta_{4l} \cdot \text{clarity}_{il}) \).

\end{align}

## Model justification
以及为什么选择gamma，因为data section 里reponse符合分布
We expect a positive relationship between the size of the wings and time spent aloft. In particular...

@@

## Model Comparision: Generalized Linear Model vs. Linear Model

## Model Evaluation
See appendix

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of Diamond Price based on Color, Cut, Clarity and Carat Size"
#| warning: false

summary(model_glm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
#| label: fig-prediction_actual
#| fig-cap: "Actual vs Predicted Values"

test_data$price <- scale(test_data$price, center = TRUE, scale = TRUE)
test_data$price<-exp(test_data$price)
test_data$color <- factor(test_data$color)
test_data$cut <- factor(test_data$cut)
test_data$clarity <- factor(test_data$clarity)

test_data$predicted_price <- predict(model_glm, newdata = test_data, type = "response")

ggplot(data = test_data, aes(x = 1:nrow(test_data))) +
  geom_line(aes(y = predicted_price), color = "lightblue", size = 1, linetype = "solid") + 
  geom_point(aes(y = price), color = "palevioletred", size = 2) + 
  labs(
    x = "Index",
    y = "Price"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

## Model Formula

## Example of Prediction

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

## Limitations
### Data Limitations
数据分布不均
### Model Limitations

## Further Considerations

@@

# Additional data details {#sec-data-details}

## Data Summary
data section
```{r}
#| echo: false
#| eval: true
#| label: tbl-cleaned data
#| tbl-cap: "First 8 rows of Cleaned data"
#| warning: false

head_cleaned_data <- head(cleaned_data,8)
knitr::kable(head_cleaned_data, format = "simple", col.names = c('Diamond Price','Carat Size','Color', 'Clarity','Cut'))

## Data Cleaning
data section
## Data Preparation and Data Split
Model Section

response variable
train test to fit the mode

@@

## Model Evaluation

@@

pp_check(model_glm) +
  theme_classic() +
  theme(legend.position = "bottom")
